---
title: "journal tf-idf"
format: 
  html:
    page-layout: full
toc: true
execute:
  echo: false
  message: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| eval: false

# setwd("/home/agricolamz/work/databases/linguistic_journals_ru/morphological_annotation/journal_tf_idf")

library(tidyverse)
library(tidytext)

read_csv("../../linguistic_journals_ru/russian_journals.csv") |> 
  left_join(read_csv("../abstracts_udpiped.csv")) |> 
  filter(is.na(remove),
         !is.na(abstract)) |> 
  filter(!(tag %in% c("textology",
                      "anthropology",
                      "education",
                      "not lingv",
                      "not linguistics",
                      "linguistic anthropology",
                      "about person/event",
                      "ethnography",
                      "archeology",
                      "history",
                      "philology", 
                      "about event",
                      "about person",
                      "about linguistics",
                      "translation studies",
                      "literary studies",
                      "other"))) |> 
  distinct()->
  merged

map(stopwords::stopwords_getsources()[-c(3, 4, 6, 8)], function(i){
  print(i)
  stopwords::stopwords(language = "ru", source = i)}) |> 
  unlist() |>  
  unique() |> 
  sort() ->
  stopwords_ru

stopwords_ru <- c(stopwords_ru, "статья", "исследование", "автор")

merged |> 
  select(journal_title, lemmatized) |> 
  unnest_tokens(output = "word", lemmatized) |> 
  count(journal_title, word, sort = TRUE) |> 
  filter(str_detect(word, "\\d", negate = TRUE)) |> 
  anti_join(tibble(word = stopwords_ru, by = "word")) |> 
  write_csv("unigram.csv")

merged |> 
  select(journal_title, lemmatized) |> 
  unnest_tokens(output = "ngram", lemmatized, token = "ngrams", n = 2) |> 
  filter(str_detect(ngram, "\\d", negate = TRUE)) |> 
  separate(ngram, into = c("first", "second"), sep = " ") |> 
  anti_join(tibble(first = stopwords_ru, by = "first")) |>
  anti_join(tibble(second = stopwords_ru, by = "second")) |>
  mutate(ngram = str_c(first, " ", second)) |> 
  count(journal_title, ngram, sort = TRUE) |> 
  write_csv("bigram.csv")
```


```{r}
suppressPackageStartupMessages(library(tidyverse))
library(tidytext)

unigrams <- read_csv("unigram.csv", show_col_types = FALSE) 
bigrams <- read_csv("bigram.csv", show_col_types = FALSE) 

unigrams |> 
  distinct(journal_title) |> 
  pull(journal_title) ->
  journals
```



## `r journals[1]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[1], journals[1], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[1]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[1], journals[1], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[1]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[2]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[2], journals[2], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[2]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[2], journals[2], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[2]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[3]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[3], journals[3], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[3]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[3], journals[3], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[3]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[4]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[4], journals[4], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[4]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[4], journals[4], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[4]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[5]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[5], journals[5], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[5]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[5], journals[5], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[5]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[6]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[6], journals[6], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[6]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[6], journals[6], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[6]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[7]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[7], journals[7], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[7]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[7], journals[7], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[7]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[8]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[8], journals[8], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[8]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[8], journals[8], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[8]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[9]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[9], journals[9], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[9]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[9], journals[9], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[9]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[10]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[10], journals[10], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[10]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[10], journals[10], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[10]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[11]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[11], journals[11], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[11]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[11], journals[11], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[11]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[12]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[12], journals[12], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[12]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[12], journals[12], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[12]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[13]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[13], journals[13], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[13]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[13], journals[13], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[13]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[14]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[14], journals[14], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[14]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[14], journals[14], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[14]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[15]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[15], journals[15], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[15]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[15], journals[15], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[15]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[16]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[16], journals[16], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[16]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[16], journals[16], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[16]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[17]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[17], journals[17], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[17]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[17], journals[17], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[17]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[18]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[18], journals[18], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[18]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[18], journals[18], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[18]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[19]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[19], journals[19], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[19]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[19], journals[19], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[19]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[20]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[20], journals[20], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[20]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[20], journals[20], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[20]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::

## `r journals[21]`

::: {.panel-tabset}

### Unigram

```{r}
unigrams |> 
  mutate(journal_title = if_else(journal_title == journals[21], journals[21], 'other')) |> 
  bind_tf_idf(word, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[21]) |> 
  select(word, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))

```

### Bigram

```{r}
bigrams |> 
  mutate(journal_title = if_else(journal_title == journals[21], journals[21], 'other')) |> 
  bind_tf_idf(ngram, journal_title, n) |> 
  arrange(desc(tf_idf)) |> 
  filter(journal_title == journals[21]) |> 
  select(ngram, n) |> 
  DT::datatable(class = 'cell-border stripe', 
    rownames = FALSE, 
    filter = 'top', 
    extensions = 'Buttons',
    options = list(pageLength = 50, 
                   autoWidth = TRUE, 
                   info = FALSE,
                   dom = 'fBtp',
                   buttons = list(list(extend = 'collection',
                                       buttons = c('csv'))),
                   paginate = TRUE))
```

:::
